\subsection*{Implicit in Time Method}
\label{sec:Q5c}

The implicit-in-time discretization is given by the equation:

\begin{equation}
    \frac{a_i^{n+1}-a_i^n}{\Delta t} = -u\frac{a_i^{n+1}-a_{i-1}^{n+1}}{\Delta x}
\label{eq:IIT}
\end{equation}

Which similar to the previous methods can be rearranged:

\begin{equation}
\begin{split}
    a_i^{n+1} & = \frac{-u \Delta t}{\Delta x} (a_{i}^{n+1} - a_{i-1}^{n+1}) + a_i^n \\
              & = - C (a_{i}^{n+1} - a_{i-1}^{n+1}) + a_i^n \\
    a_i^n &= -C a_{i-1}^{n+1} + (1+C) a_{i}^{n+1}
\end{split}
\label{eq:IIT_a}
\end{equation}

Which when written in matrix form is generally given as:

\begin{equation}
\begin{pmatrix}
1+C &     &     &        &        &     & -C  \\
-C  & 1+C &     &        &        &     &     \\
    & -C  & 1+C &        &        &     &     \\
    &     & -C  & 1+C    &        &     &     \\
    &     &     & \ddots & \ddots &     &     \\
    &     &     &        & -C     & 1+C &     \\
    &     &     &        &        & -C  & 1+C \\
\end{pmatrix}
\begin{pmatrix}
u_1^{n+1}     \\
u_2^{n+1}     \\
u_3^{n+1}     \\
u_4^{n+1}     \\
\vdots        \\
u_{N-2}^{n+1} \\
u_{N-1}^{n+1} \\
\end{pmatrix}
=
\begin{pmatrix}
u_1^{n}     \\
u_2^{n}     \\
u_3^{n}     \\
u_4^{n}     \\
\vdots      \\
u_{N-2}^{n} \\
u_{N-1}^{n} \\
\end{pmatrix}
\end{equation}

To solve for $B$ in an equation of the form $AB = X$  we must take the inverse of $A$ and perform $A^{-1}AB = A^{-1}X$ which becomes $B = A^{-1}X$. We can find the inverse of our matrix using the Gauss-Jordan elimination Method. To do this we append an identity matrix to the matrix which we wish to invert. From here we use basic row operations to change our matrix $A$ into row-echelon form. This will also apply the operations to the identity matrix which once our matrix $A$ is in row-echelon form, the right hand matrix will be $A^{-1}$.

\begin{equation*}
\left(
\begin{array}{@{}ccccc|ccccc@{}}
1+C &        &        &     & -C  & 1 &   &        &   &   \\
-C  & 1+C    &        &     &     &   & 1 &        &   &   \\
    & \ddots & \ddots &     &     &   &   & \ddots &   &   \\
    &        & -C     & 1+C &     &   &   &        & 1 &   \\    
    &        &        & -C  & 1+C &   &   &        &   & 1 \\    
\end{array}
\right)
\end{equation*}

By doing this we can produce figures \ref{fig:IIT_dx005}, \ref{fig:IIT_dx003} and \ref{fig:IIT_dx001}. Similar to the upwind method, the implicit-in-time method produces a stable solution. Again if we perform a similar analysis as with the upwind method we can see that a numeric diffusion term is present. 

\begin{equation}
\begin{split}
     \frac{a_i^{n+1} - a_i^n}{\Delta t} &= -u \frac{a_i^{n+1} - a_{i-1}^{n+1}}{\Delta x} \\
                                        &= -u \left(\frac{a_{i+1}^{n+1} - a_{i-1}^{n+1}}{2\Delta x} - \Delta x \frac{(a_{i+1}^{n+1} - 2a_i^{n+1} + a_{i-1}^{n+1})}{2\Delta x^2} \right) \\
                                        &= -u \frac{(a_{i+1}^{n+1}- a_{i-1}^{n+1})}{2\Delta x} + \frac{u \Delta x}{2} \frac{(a_{i+1}^{n+1} - 2a_i^{n+1} + a_{i-1}^{n+1})}{\Delta x^2} \\
                                        &= -u \frac{(a_{i+1}^{n+1} - a_{i-1}^{n+1})}{2\Delta x} + D \frac{(a_{i+1}^{n+1} - 2a_i^{n+1} + a_{i-1}^{n+1})}{\Delta x^2} 
\end{split}
\label{eq:IIT_diff}
\end{equation}

The effect of the resolution is again apparent with lower resolution producing a more diffuse solution with the diffusion term being represented by $D = \frac{u\Delta x}{2}$. The key difference between the implicit-in-time solution and the upwind solution is that the CFL number has a smaller effect in the implicit-in-time method. While changes in the CFL number resulted in significant changes in $a$ for the upwind method, there is a much smaller difference in the implicit-in-time method. Another difference is that the higher CFL number produces smaller $a$ values in the implicit-in-time method instead of larger $a$ values in the upwind method.